% ============================================================
% One-page Flyer / Announcement (LaTeX) — modern, professional
% Colloquium: Hard Problems in Cryptography
% ============================================================
\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{array}
\usepackage{tabularx}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

% ---------- Fill these in ----------
\newcommand{\titleline}{Hard Problems in Cryptography — Colloquium}
\newcommand{\term}{[Insert dates / term]}
\newcommand{\whenwhere}{[Day, time] · [Room] / Zoom: [link]}
\newcommand{\organizer}{[Your name]}
\newcommand{\contact}{[Email]}
\newcommand{\signup}{[Sign-up link]}
\newcommand{\deadline}{[Sign-up deadline]}
\newcommand{\repo}{[Shared notes link]}
\newcommand{\audience}{Masters / advanced undergrad; PhD welcome}

% ---------- Minimal modern styling ----------
\definecolor{ink}{RGB}{20,23,28}
\definecolor{muted}{RGB}{90,96,105}
\definecolor{accent}{RGB}{34,91,191}

\begin{document}
	\color{ink}
	
	% ---------- Header block ----------
	{\Large\bfseries \titleline}\\[-2pt]
	{\color{muted}\term}\\[6pt]
	
	\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}
		Meetings: & \whenwhere\\
		Organizer: & \organizer\ (\contact)\\
		Sign-up: & \signup \hfill \textbf{Deadline:} \deadline\\
		Notes/Repo: & \repo\\
	\end{tabularx}
	
	\vspace{10pt}
	{\color{accent}\rule{\textwidth}{1.2pt}}
	\vspace{10pt}
	
	% ---------- Body ----------
	\textbf{Overview}\\
	A weekly, participant-led colloquium on the computational problems that support modern cryptography and post-quantum designs.
	Each session pairs a short talk with a working discussion: we focus on precise problem statements, the core ideas behind major attacks, and what drives parameter choices.
	
	\textbf{Who it’s for}\\
	\audience. Comfort with modular arithmetic, basic linear algebra, and proof writing is enough. A short preliminaries handout will be provided.
	
	\textbf{Format (90 minutes)}
	\begin{itemize}[leftmargin=1.6em,itemsep=2pt,topsep=2pt]
		\item \textbf{Talk (30--40 min)} — rotating presenters, with a shared template
		\item \textbf{Working session (35--45 min)} — proof sketches + toy instances + attack walk-throughs
		\item \textbf{Discussion (10--15 min)} — assumptions, sharp edges, and open questions
	\end{itemize}
	
	\textbf{Planned themes}\\
	Integer factorization (RSA/Rabin), discrete logarithms (finite fields and elliptic curves), lattices (SVP/CVP, SIS/LWE), code-based decoding (ISD),
	isogenies, multivariate quadratic systems (MQ), and hash-function security (collision/preimage, Merkle--Damg{\aa}rd/HMAC, quantum impact).
	
	\textbf{Participation}\\
	Presenting is encouraged but optional. Presenters will receive a lightweight checklist (definition + one reduction/equivalence + one attack mechanism + two practice problems).
	Everyone contributes questions in advance and helps maintain a clean shared set of notes.
	
	\vfill
	{\color{muted}\small
		\textbf{Note.} This is an educational research-reading group. We focus on publicly documented algorithms and standard security models.}
	
\end{document}
