\chapter{Mathematical Typesetting}

\section{Why LaTeX is Powerful for Mathematics}

One of the strongest reasons to use LaTeX is its ability to typeset mathematics clearly and professionally. Mathematical notation in LaTeX is precise, readable, and consistent across documents.

\section{Inline and Display Mathematics}

\subsection{Inline Mathematics}

Inline mathematics is used inside a sentence and must be enclosed in dollar signs.  
For example, the famous equation $E = mc^2$ appears naturally within text.

\begin{example}
	The quadratic polynomial $ax^2 + bx + c$ has degree $2$.
\end{example}

\subsection{Displayed Mathematics}

Displayed mathematics is used for important equations that appear on their own line.

\begin{equation}
	E = mc^2
\end{equation}

\section{Superscripts and Subscripts}

\begin{itemize}
	\item Superscripts use the caret symbol: $x^2$, $a^{n+1}$
	\item Subscripts use the underscore symbol: $a_1$, $b_{ij}$
\end{itemize}

\begin{example}
	The sequence $a_n = n^2$ grows quadratically.
\end{example}

\section{Fractions and Roots}

\begin{itemize}
	\item Fractions: $\frac{a}{b}$
	\item Nested fractions: $\frac{1}{1 + \frac{1}{x}}$
	\item Square roots: $\sqrt{2}$
	\item General roots: $\sqrt[n]{x}$
\end{itemize}

\begin{example}
	The solution is $x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}$.
\end{example}

\section{Greek Letters}

Greek letters are frequently used in mathematics and science.

\begin{itemize}
	\item Lowercase: $\alpha$, $\beta$, $\gamma$, $\delta$, $\epsilon$
	\item Uppercase: $\Gamma$, $\Delta$, $\Theta$, $\Lambda$
\end{itemize}

\section{Common Mathematical Symbols}

\begin{itemize}
	\item Summation: $\sum_{i=1}^{n} i$
	\item Product: $\prod_{k=1}^{n} k$
	\item Integrals: $\int_0^1 x^2 \, dx$
	\item Limits: $\lim_{x \to 0} \frac{\sin x}{x}$
\end{itemize}

\section{Aligned Equations}

Use the \texttt{align} environment to align multiple equations.

\begin{align}
	x + y &= 10 \\
	2x - y &= 3
\end{align}

\section{Matrices}

Matrices are written using matrix environments.

\begin{equation}
	A =
	\begin{pmatrix}
		1 & 2 \\
		3 & 4
	\end{pmatrix}
\end{equation}

\section{Cases}

Piecewise-defined functions use the \texttt{cases} environment.

\begin{equation}
	f(x) =
	\begin{cases}
		x^2, & x \geq 0 \\
		-x, & x < 0
	\end{cases}
\end{equation}

\section{Exercise}

\begin{exercise}
	Typeset the following in LaTeX:
	\begin{itemize}
		\item The binomial formula $(a+b)^2 = a^2 + 2ab + b^2$
		\item A $2 \times 3$ matrix
		\item The definite integral $\int_0^\pi \sin x \, dx$
		\item A piecewise function with two cases
	\end{itemize}
\end{exercise}
