\documentclass[11pt,openany]{article}

\input{grad-math-preamble}
\input{tcolorbox}
\input{theorem}
\input{tikz}
\input{grad-math-commands}

\setstretch{1.25}
\begin{document}
\pagenumbering{arabic}
\begin{center}
	\huge\textbf{Advanced Calculus II}\\
	\vspace{0.5em}
	\large{Ji, Yong-hyeon}\\
	\vspace{0.5em}
	\normalsize{\today}\\
\end{center}

\noindent 
We cover the following topics in this note.
\begin{itemize}
	\item Convergence of Real Sequences
	\item Inequality Rule for Real Sequences
	\item Limit Theorems for Real Sequences
\end{itemize}
\hrule\vspace{12pt}
%Preliminaries:
%\begin{itemize}
%	\item Boundedness, Supremum and Infimum
%	\item Least Upper Bound Property (Completeness Axiom)
%	\item Well-Ordering Principle and Mathematical Induction
%	\item Archimedean Property
%\end{itemize}
%\hrule\vspace{12pt}


\newpage
%\tableofcontents
\vfill
\defbox[Sequence]{\begin{definition*}
	A \textbf{real sequence}(or a sequence in $\R$) is a function defined on the set N
	whose range is contained in the set $\R$.
\end{definition*}}
\begin{remark*}
A function $a$ is a real sequence if \[
\fullfunction{a}{\N}{\R}{n}{a(n)=:a_n}
\] for $n=1,2,\cdots$. We write $
\set{a_n}_{n=1}^{\infty} (\text{or} \set{a_n})$.
\end{remark*}
\begin{tcolorbox}[colback=white]
	\begin{definition}[\bf Convergence]
		A real sequence $\set{a_n}$ is said to converge to $L\in\R $ or $L$ is said to be a limit of $\set{a_n}$,
		if $\forall\varepsilon>0$, $\exists N(\varepsilon)\in\N$ such that \[
		n\geq N(\varepsilon)\implies \abs{a_n-L}<\varepsilon.
		\]
		If a sequence has a limit, we say that the sequence is convergent; if it has no limit, we say that the
		sequence is divergent.
	\end{definition}
\end{tcolorbox}
\begin{remark}
	\begin{align*}
		\lim_{n\to\infty}a_n=L&\iff \forall\varepsilon>0,\ \exists N(\varepsilon)\in\N\ \text{such that}\ n\geq N(\varepsilon)\implies \abs{a_n-L}<\varepsilon\\
		&\iff\forall\varepsilon>0,\ \#\set{n\in\N: a_n\not\in(x-\varepsilon,x+\varepsilon)}<\infty.
	\end{align*}
\end{remark}
\begin{remark}
	We can abbreviate $\lim\limits_{n\to\infty}a_n=L$ to $a_n\to L$.
\end{remark}

\begin{tcolorbox}[colback=white]
	\begin{definition}[\bf Divergence]
		Let $\set{a_n}$ be a real sequence. We say that \begin{itemize}
			\item $\set{a_n}$ \textbf{diverges to infinity}(or \textbf{tends to infinity}) if $\forall M\in\R,\ \exists N\in\N$ such that \[
			n\geq N\implies a_n>M
			\] and write \[
			\lim_{n\to\infty}a_n=+\infty.
			\]
			\item $\set{a_n}$ \textbf{diverges to minus infinity}(or \textbf{tends to minus infinity}) if $\forall M\in\R,\ \exists N\in\N$ such that \[
			n\geq N\implies a_n<M
			\] and write \[
			\lim_{n\to\infty}a_n=-\infty.
			\]
			\item $\set{a_n}$ is \textbf{properly divergent} in case we have either \[
			\lim_{n\to\infty}a_n=-\infty\ \text{or}\ \lim_{n\to\infty}a_n=-\infty.
			\]
		\end{itemize}
	\end{definition}    
\end{tcolorbox}
\begin{remark}
	\begin{align*}
		\lim_{n\to\infty}a_n=+\infty&\iff \forall M\in\R,\ \exists N\in\N\ \text{such that}\ n\geq N\implies M<a_n\\
		\lim_{n\to\infty}a_n=-\infty&\iff \forall M\in\R,\ \exists N\in\N\ \text{such that}\ n\geq N\implies a_n<M.
	\end{align*}
\end{remark}

\subsection{Theorems 1}
\begin{tcolorbox}[colback=white]
	\begin{theorem}[\bf Uniqueness of Limits]
		The limit of a real sequence is unique.
	\end{theorem}
\end{tcolorbox}\begin{proof}
	Let a real sequence $\set{a_n}$ has limit $L_1$ and $L_2$, and let $\varepsilon>0$. Since $\lim\limits_{n\to\infty}a_n=L_1$, \[
	\exists N_1\in\N: n\geq N_1\implies\abs{a_n-L_1}<\frac{\varepsilon}{2}.
	\]Also we have \[
	\exists N_2\in\N: n\geq N_2\implies\abs{a_n-L_2}<\frac{\varepsilon}{2}.
	\] Let $N=\max\set{N_1,N_2}$, then if $n\geq N$, \begin{align*}
		\abs{L_2-L_1}&=\abs{L_2-L_1+a_n-a_n}\\
		&=\abs{(a_n-L_1)-(a_n-L_2)}\\
		&\leq\abs{a_n-L_1}+\abs{a_n-L_2} \quad(\because \abs{a-b}\leq\abs{a}+\abs{b})\\
		&<\frac{\varepsilon}{2}+\frac{\varepsilon}{2}=\varepsilon.
	\end{align*}
\end{proof}
\begin{remark}
	Let $\lim\limits_{n\to\infty}$ is a function as $\lim\limits_{n\to\infty}:F_{\text{Con}}\footnote{$F_{\text{Con}}:=\set{\text{Convergent sequences on $\R$}}$}\to\R$ given by \[
	\set{a_n}\mapsto\lim_{n\to\infty}a_n.
	\] Then \[
	\set{a_n}=\set{b_n}\implies \lim_{n\to\infty}a_n=\lim_{n\to\infty}b_n,
	\] that is, $\lim\limits_{n\to\infty}$ preserves ``equality($=$)''.
\end{remark}


\vfill
\begin{thebibliography}{9}
	\bibitem{advanced_calc_c}
	수학의 즐거움, Enjoying Math. ``수학 공부, 기초부터 대학원 수학까지, 6. 해석학 개론 (c) 수열의 수렴성.'' YouTube Video, 26:29. Published 
	September 20, 2019. URL: \url{https://www.youtube.com/watch?v=jwLfzJyIxmU}.
	\bibitem{advanced_calc_d}
	수학의 즐거움, Enjoying Math. ``수학 공부, 기초부터 대학원 수학까지, 7. 해석학 개론 (d) 극한 정리'' YouTube Video, 26:46. Published 
	September 26, 2019. URL: \url{https://www.youtube.com/watch?v=1TRD34QbIaw}.
\end{thebibliography}

%\newpage
%\appendix
\end{document}
