\section{Introduction to \LaTeX}
\LaTeX{} (often pronounced “Lay-tek” or “Lah-tek”) is a high-quality typesetting system widely used for professional scientific and technical documents.

Instead of formatting text by hand (like in a word processor), we write a plain-text source file and then \emph{compile} it into a polished PDF.

\subsection{What is \LaTeX?}
\begin{tcolorbox}[colback=white, title={What is \LaTeX?}, colframe=teal]
\LaTeX{} is a document preparation system based on \TeX{}, designed for producing beautifully typeset documents, especially those containing complex mathematical expressions.
\end{tcolorbox}
A helpful way to think about \LaTeX{} is:
\begin{itemize}
\item We write \emph{content} and \emph{structure} (sections, theorems, figures, references).
\item The compiler applies consistent typography and layout rules automatically.
\end{itemize}
This separation makes long documents easier to maintain: if we change the structure (add sections, figures, equations), numbering and references can update automatically when compiled again.

\paragraph{What \TeX{} and \LaTeX{} Do}

\begin{itemize}
\item \TeX{} is the underlying typesetting engine (it focuses on high-quality layout and spacing).
\item \LaTeX{} is a set of macros and conventions on top of \TeX{} that provides document structure:
chapters/sections, figures, tables, bibliographies, and many more.
\end{itemize}
We usually write \LaTeX{} source and let the engine produce the final PDF.

\paragraph{Why Use \LaTeX?}

People choose \LaTeX{} because it is strong where word processors often become difficult:
\begin{itemize}
\item \underline{\textbf{Professional-quality typography}} with consistent formatting across the whole document.
\item \underline{\textbf{Excellent mathematical rendering}}, for example $a^2 + b^2 = c^2$ and complex formulas.
\item \underline{\textbf{Automatic numbering and references}} for equations, figures, sections, and bibliographies.
\item \underline{\textbf{Scales well}} to long reports, theses, and books: structure stays manageable.
\end{itemize}

\paragraph{When \LaTeX{} Is a Good Fit}

\begin{itemize}
\item Math-heavy documents (homework, lecture notes, papers).
\item Reports with many figures/tables and cross-references.
\item Theses and books with chapters and bibliographies.
\end{itemize}

\paragraph{When It Might Not Be Necessary}

\begin{itemize}
\item Very short, simple documents where structure and references do not matter.
\item Layout-heavy marketing designs (unless you already know advanced packages).
\end{itemize}

\subsubsection{Compiling a Document}

A \LaTeX{} file is typically saved with the extension \texttt{.tex}. To produce a PDF, you run a compiler (engine) that reads the source and outputs the final document.

\paragraph{The Basic Compile Command}

A common engine is \texttt{pdflatex}. The typical workflow is:
\begin{lstlisting}
pdflatex file.tex
pdflatex file.tex  % run twice to update references
\end{lstlisting}
Running twice matters because references (like section numbers, equation numbers, and the table of contents) are resolved across compilation passes.

\paragraph{What Happens During Compilation}

When you compile, \LaTeX{}:
\begin{itemize}
\item reads your structure (chapters, sections, lists),
\item calculates layout (line breaks, page breaks),
\item assigns numbers (figures, tables, equations),
\item writes auxiliary files (used to resolve references),
\item produces a PDF output.
\end{itemize}

\paragraph{Recommended Tools}

We can write and compile \LaTeX{} using:
\begin{itemize}
\item \textbf{Overleaf}: online editor; no installation required.
\item \textbf{TeX Live}: a full \TeX{} distribution commonly used on Linux/macOS.
\item \textbf{MiKTeX}: a popular distribution on Windows.
\end{itemize}

%\subsection{Simple Example}
%Every \LaTeX{} document has two major parts:
%\begin{itemize}
%	\item A \textbf{setup part} (before \verb|\begin{document}|): selects the document type and loads packages.
%	\item The \textbf{content part} (between \verb|\begin{document}| and \verb|\end{document}|):  actual text, math, figures, etc.
%\end{itemize}
%The reference notes show a typical skeleton that includes common packages like math, graphics, and hyperlinks. Here is a beginner-friendly version:
%
%\begin{example}[Template]
%\;
%
%\medskip
%
%\begin{lstlisting}
%\documentclass[11pt]{article}
%\usepackage{amsmath,amssymb}
%\usepackage{graphicx}
%\usepackage{hyperref}
%
%\title{My First LaTeX Document}
%\author{Student Name}
%\date{\today}
%
%\begin{document}
%	\maketitle
%	
%	This is a sentence with inline math: $a^2 + b^2 = c^2$.
%	
%\end{document}
%\end{lstlisting}
%\end{example}