% pdflatex -shell-escape software-analysis-main.tex
\documentclass[12pt,openany]{book}

\input{preamble/mm-package}
\input{preamble/mm-theorem}
\input{preamble/mm-layout}
\input{preamble/mm-tcolorbox}
\input{preamble/mm-tikz}
\input{preamble/mm-algorithm}
\input{preamble/mm-listing}
\input{preamble/mm-commands}


\begin{document}
	
	\input{mm-titlepage}
	\tableofcontents
	\newpage
	\chapter{Introduction}
	\input{chapter/mm-chap1}
	
	\newpage
	\chapter{Quadratic Formula and Peano Axiom}
	\input{chapter/mm-chap2}
	
	\newpage
	\chapter{Functions}
	\input{chapter/mm-chap3}
	
	\newpage
	\chapter{Group Homomorphism}
	\input{chapter/mm-chap4}
	
	\newpage
	\chapter{Linear Algebra and Group}
	\input{chapter/mm-chap5}
	
	From the standpoint of solving equations, the algebraic structures we have discussed are interconnected in the following ways:
	
	\subsection*{Group}
	A \textbf{group} provides a foundation for solving equations involving a single operation. The group structure ensures that every element has an inverse, allowing us to "undo" operations and solve equations. For instance, in the group of integers \( (\mathbb{Z}, +) \), the equation \( x + a = b \) can be solved as \( x = b - a \).
	
	\subsection*{Ring}
	A \textbf{ring} extends the concept of a group by introducing a second operation, typically multiplication, in addition to addition. Rings allow us to solve more complex equations that involve both addition and multiplication. For example, solving polynomial equations \( f(x) = 0 \) where \( f(x) \) is a polynomial with coefficients in a ring \( R \).
	
	\subsection*{Field}
	A \textbf{field} is a ring with additional properties that make division possible (except by zero). This structure is crucial for solving linear equations and systems of linear equations. In a field \( F \), any linear equation \( ax = b \) (where \( a \neq 0 \)) can be solved as \( x = a^{-1}b \), where \( a^{-1} \) is the multiplicative inverse of \( a \).
	
	\subsection*{Vector Space}
	A \textbf{vector space} over a field \( F \) is a set of vectors that can be added together and scaled by elements of \( F \). Vector spaces provide a framework for solving linear systems of equations. Solutions to systems of linear equations can be understood as finding vectors \( \mathbf{x} \in V \) such that \( A\mathbf{x} = \mathbf{b} \), where \( A \) is a matrix and \( \mathbf{b} \) is a vector in \( V \).
	
	\subsection*{Module}
	A \textbf{module} is a generalization of vector spaces where the scalars come from a ring instead of a field. Modules allow us to solve equations in contexts where the coefficients are not from a field, such as systems of linear equations with integer coefficients. For example, solving \( A\mathbf{x} = \mathbf{b} \) where \( A \) is a matrix with entries from a ring \( R \) and \( \mathbf{x}, \mathbf{b} \in M \).
	
	\subsection*{Algebra}
	An \textbf{algebra} over a field \( F \) combines the structures of a vector space and a ring. Algebras provide a framework for solving polynomial equations and other equations involving both addition and multiplication of vectors. In an algebra \( A \), we can solve equations like \( x^2 + ax + b = 0 \) using techniques from both linear algebra and ring theory.
	
	\subsection*{Summary}
	The conceptual connection between these structures is rooted in the increasing complexity and capability they offer for solving equations:
	\begin{itemize}
		\item \textbf{Groups} provide a way to solve equations with a single operation.
		\item \textbf{Rings} introduce a second operation, allowing for more complex equations.
		\item \textbf{Fields} enable division, which is essential for solving linear equations.
		\item \textbf{Vector spaces} over fields extend these concepts to systems of linear equations.
		\item \textbf{Modules} generalize vector spaces to allow coefficients from rings.
		\item \textbf{Algebras} integrate vector space and ring structures, enabling the solution of polynomial and other complex equations.
	\end{itemize}
	
	\newpage
	\chapter*{LaTex Practice}
	\input{latex-practice}
	
	% Appendix
	\newpage
	\appendix
	\input{appendix/mm-appendix-A}
	
\end{document}
