\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\newcommand{\C}{\mathbb{C}}
\newcommand{\CP}{\mathbb{CP}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\Res}{\operatorname{Res}}
\newcommand{\Divv}{\operatorname{Div}}

\begin{document}
	
	\title{Concrete, calculus-style examples of \(\M(X)\) for \(X=\CP^1\) and \(X=\C/\Lambda\)}
	\author{}
	\date{}
	\maketitle
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Case 1: \(X=\CP^1\) (Riemann sphere)}
	
	\subsection{Setup: coordinate and function field}
	
	View \(\CP^1\) as the Riemann sphere:
	\[
	\CP^1 \cong \C \cup \{\infty\}.
	\]
	Use the standard affine coordinate
	\[
	z = \frac{z_0}{z_1}
	\]
	on the chart \(U_1 = \{[z_0:z_1]\mid z_1\neq 0\}\cong \C\).
	The point at infinity is
	\[
	\infty = [1:0].
	\]
	
	A meromorphic function on \(\CP^1\) is the same as a rational function in \(z\), i.e.
	\[
	\M(\CP^1) \cong \C(z).
	\]
	
	We will \emph{explicitly} analyze one such function and its differential.
	
	\subsection{A concrete meromorphic function \(f\) on \(\CP^1\)}
	
	Let
	\[
	f(z) = \frac{(z-1)^2}{z(z-2)}.
	\]
	
	\subsubsection*{Step 1: Zeros and poles on \(\C\)}
	
	\begin{itemize}
		\item Zeros (where numerator vanishes):
		\[
		(z-1)^2 = 0 \quad\Rightarrow\quad z=1\quad\text{(double zero)}.
		\]
		So \(\operatorname{ord}_{z=1}(f) = +2\).
		
		\item Poles (where denominator vanishes):
		\[
		z(z-2)=0 \quad\Rightarrow\quad z=0,\ z=2.
		\]
		We check they are simple poles:
		
		Near \(z=0\): write \(z\) as local coordinate. Then
		\[
		f(z) = \frac{(z-1)^2}{z(z-2)}
		= \frac{z^2 - 2z + 1}{z(z-2)}
		\sim \frac{1}{z(-2)} = -\frac{1}{2z}
		\quad\text{as }z\to 0.
		\]
		So
		\[
		\operatorname{ord}_{z=0}(f) = -1.
		\]
		
		Near \(z=2\): set \(u = z-2\), so \(z = 2+u\). Then
		\[
		f(z) = f(2+u)
		= \frac{(2+u-1)^2}{(2+u)(2+u-2)}
		= \frac{(1+u)^2}{(2+u)u}
		\sim \frac{1}{2u}
		\quad\text{as }u\to 0.
		\]
		So
		\[
		\operatorname{ord}_{z=2}(f) = -1.
		\]
	\end{itemize}
	
	So on the finite plane:
	\[
	\operatorname{ord}_1(f) = +2,\quad
	\operatorname{ord}_0(f) = -1,\quad
	\operatorname{ord}_2(f) = -1.
	\]
	
	\subsubsection*{Step 2: Behavior at infinity via differential-calculus change of variable}
	
	To study \(z=\infty\), use \(w = 1/z\) as local coordinate near \(\infty\).
	
	Then \(z = 1/w\), and
	\[
	f(z) = f\Bigl(\frac{1}{w}\Bigr).
	\]
	
	Compute explicitly:
	\[
	f\Bigl(\frac{1}{w}\Bigr)
	= \frac{(1/w - 1)^2}{(1/w)(1/w - 2)}
	= \frac{(1-w)^2}{\frac{1}{w^2} (1 - 2w)} 
	= (1-w)^2 \cdot \frac{w^2}{1-2w}.
	\]
	Now expand near \(w=0\). First,
	\[
	(1-w)^2 = 1 - 2w + w^2,
	\]
	and
	\[
	\frac{1}{1-2w} = 1 + 2w + 4w^2 + O(w^3).
	\]
	So
	\[
	f\Bigl(\frac{1}{w}\Bigr)
	= w^2\,(1 - 2w + w^2)\,(1 + 2w + 4w^2 + O(w^3)).
	\]
	
	Multiply out just enough terms to see the leading behavior:
	\[
	(1 - 2w + w^2)(1 + 2w + 4w^2)
	= 1 + (2w - 2w) + (\cdots) = 1 + O(w^2),
	\]
	so overall
	\[
	f\Bigl(\frac{1}{w}\Bigr)
	= w^2\,(1 + O(w^2)) = w^2 + O(w^4).
	\]
	
	Thus near \(w=0\), \(f(1/w)\) has a \emph{zero of order 2} as a function of \(w\). But remember: the order at \(\infty\) as a point of \(\CP^1\) is the order of this function viewed on the sphere. More directly: in terms of the original coordinate \(z\), we see that as \(|z|\to\infty\),
	\[
	f(z) = 1 + O\Bigl(\frac{1}{z^2}\Bigr),
	\]
	so \(f\) is holomorphic and nonzero at \(\infty\). Hence
	\[
	\operatorname{ord}_{\infty}(f) = 0.
	\]
	
	\subsubsection*{Step 3: The divisor of \(f\)}
	
	The divisor of \(f\) on \(\CP^1\) is
	\[
	\Divv(f) = 2\cdot(1) - (0) - (2) + 0\cdot(\infty).
	\]
	Sum of coefficients:
	\[
	2 - 1 - 1 + 0 = 0,
	\]
	which matches the general fact that the sum of orders of a meromorphic
	function on a compact Riemann surface is zero.
	
	\subsection{Differential: computing \(df = f'(z)\,dz\) in detail}
	
	Now do calculus: compute the derivative.
	
	\subsubsection*{Step 1: Simplify \(f\) via partial fractions}
	
	We try to write
	\[
	f(z) = A + \frac{B}{z} + \frac{C}{z-2}.
	\]
	
	Compute directly:
	\[
	\frac{(z-1)^2}{z(z-2)}
	= \frac{z^2 - 2z + 1}{z(z-2)}.
	\]
	We look for \(A,B,C\) such that
	\[
	\frac{z^2 - 2z + 1}{z(z-2)}
	= A + \frac{B}{z} + \frac{C}{z-2}.
	\]
	
	Multiply both sides by \(z(z-2)\):
	\[
	z^2 - 2z + 1 = A z(z-2) + B(z-2) + Cz.
	\]
	Expand the right-hand side:
	\[
	A z(z-2) = A(z^2 - 2z) = A z^2 - 2A z,
	\]
	\[
	B(z-2) = Bz - 2B,
	\]
	\[
	Cz = Cz.
	\]
	So
	\[
	A z^2 - 2A z + Bz - 2B + Cz
	= A z^2 + (-2A + B + C)z - 2B.
	\]
	Equate coefficients with the left side \(z^2 - 2z + 1\):
	\[
	\begin{cases}
		A = 1,\\
		-2A + B + C = -2,\\
		-2B = 1.
	\end{cases}
	\]
	From \(-2B=1\), we get \(B = -\frac{1}{2}\). Then
	\[
	-2A + B + C = -2\quad\Rightarrow\quad
	-2(1) - \frac{1}{2} + C = -2
	\quad\Rightarrow\quad
	-2.5 + C = -2
	\quad\Rightarrow\quad
	C = \frac{1}{2}.
	\]
	So
	\[
	f(z) = 1 - \frac{1}{2z} + \frac{1}{2(z-2)}.
	\]
	
	\subsubsection*{Step 2: Differentiate term by term}
	
	Now
	\[
	f(z) = 1 - \frac{1}{2z} + \frac{1}{2(z-2)}.
	\]
	Differentiate:
	\[
	f'(z) = 0 + \frac{1}{2z^2} - \frac{1}{2(z-2)^2}.
	\]
	So the meromorphic 1-form
	\[
	df = f'(z)\,dz = \left( \frac{1}{2z^2} - \frac{1}{2(z-2)^2} \right)\,dz.
	\]
	
	\paragraph{Poles of \(df\).}
	Clearly:
	\[
	df \text{ has poles of order 2 at } z=0 \text{ and } z=2.
	\]
	No simple pole terms appear in the Laurent expansions; hence all residues are 0.
	
	\paragraph{Check residues explicitly via Laurent series.}
	
	Near \(z=0\):
	\[
	\frac{1}{2z^2} - \frac{1}{2(z-2)^2}
	= \frac{1}{2z^2} - \frac{1}{2(4 - 4z + z^2)}
	= \frac{1}{2z^2} - \frac{1}{8}\cdot\frac{1}{1 - z + z^2/4}.
	\]
	Expand \(\frac{1}{1 - z + z^2/4}\) as a power series in \(z\) (no negative powers),
	so near \(z=0\) this second term has no negative-power part. Thus the only
	negative-power part is \(\frac{1}{2z^2}\), which has no \((z-0)^{-1}\) term.
	So \(\Res_{z=0}(df) = 0\).
	
	Similarly near \(z=2\), set \(u=z-2\). Then
	\[
	df = \left( \frac{1}{2(2+u)^2} - \frac{1}{2u^2} \right)\,d(2+u)
	= \left( \frac{1}{8}\cdot\frac{1}{(1+u/2)^2} - \frac{1}{2u^2} \right)\,du.
	\]
	Again the first term has only nonnegative powers in \(u\), the second has
	\(u^{-2}\) but no \(u^{-1}\). So \(\Res_{z=2}(df)=0\).
	
	At \(\infty\), we could check via \(w=1/z\). A general fact: for any meromorphic function \(f\) on a compact Riemann surface,
	\[
	\sum_p \Res_p(df) = 0.
	\]
	Since the residues at \(0\) and \(2\) are zero, the residue at \(\infty\) is
	also zero.
	
	\subsection{Moral for \(\CP^1\): function field via differential forms}
	
	In general, if \(f\) is \emph{any} meromorphic function on \(\CP^1\), then
	
	\begin{itemize}
		\item \(df\) is a meromorphic 1-form whose residues all vanish.
		\item By analyzing the principal parts and using Liouville, one shows that
		\(f\) must be a rational function in the coordinate \(z\).
	\end{itemize}
	
	Thus the function field is
	\[
	\M(\CP^1) = \C(z).
	\]
	
	Our explicit \(f\) shows concretely how poles/zeros and the differential look,
	and how partial fractions naturally appear from calculus.
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Case 2: \(X=\C/\Lambda\) (complex torus)}
	
	Now we move to a more subtle example and use differential forms very concretely.
	
	\subsection{The torus and the basic holomorphic 1-form}
	
	Let \(\Lambda\subset\C\) be a lattice:
	\[
	\Lambda = \mathbb{Z}\omega_1 \oplus \mathbb{Z}\omega_2,\quad
	\Im\left(\frac{\omega_2}{\omega_1}\right) > 0.
	\]
	Define the complex torus
	\[
	X = \C/\Lambda.
	\]
	
	The projection \(\pi:\C\to X\) is holomorphic and locally biholomorphic.
	The 1-form \(dz\) on \(\C\) is invariant under translations by \(\Lambda\), so it
	descends to a global holomorphic 1-form on \(X\). In fact,
	\[
	H^0(X,\Omega^1_X) = \C\cdot dz,
	\]
	i.e.\ there is a one-dimensional space of holomorphic 1-forms.
	
	\subsection{The Weierstrass \(\wp\) and its derivative \(\wp'\)}
	
	Define the Weierstrass \(\wp\)-function:
	\[
	\wp(z) = \frac{1}{z^2}
	+ \sum_{\lambda\in\Lambda\setminus\{0\}}
	\left(
	\frac{1}{(z-\lambda)^2} - \frac{1}{\lambda^2}
	\right).
	\]
	Facts:
	\begin{itemize}
		\item \(\wp(z+\lambda) = \wp(z)\) for all \(\lambda\in\Lambda\)
		(\(\Lambda\)-periodic).
		\item \(\wp\) is even: \(\wp(-z)=\wp(z)\).
		\item \(\wp\) is meromorphic on \(\C\) with poles of order 2 at each
		lattice point.
	\end{itemize}
	
	Differentiate term by term (justified by uniform convergence on compact
	sets away from poles):
	\[
	\wp'(z)
	= -\frac{2}{z^3}
	- 2\sum_{\lambda\in\Lambda\setminus\{0\}}
	\frac{1}{(z-\lambda)^3}.
	\]
	Then:
	\begin{itemize}
		\item \(\wp'\) is odd: \(\wp'(-z)=-\wp'(z)\).
		\item \(\wp'(z)\) has poles of order 3 at each lattice point.
	\end{itemize}
	
	Both \(\wp\) and \(\wp'\) are \(\Lambda\)-periodic, so they descend to meromorphic
	functions on \(X=\C/\Lambda\):
	\[
	\wp_X([z]) = \wp(z),\qquad (\wp_X)'([z]) = \wp'(z).
	\]
	
	\subsection{The meromorphic 1-form \(\wp'(z)\,dz = d\wp(z)\)}
	
	Consider the 1-form
	\[
	\omega = \wp'(z)\,dz.
	\]
	This is clearly
	\[
	\omega = d\wp(z),
	\]
	as in calculus: derivative times \(dz\).
	
	\subsubsection*{Local expansion near a pole}
	
	Focus on the point \([0]\in X\) (the image of \(0\in\C\)).
	
	Near \(z=0\),
	\[
	\wp(z) = \frac{1}{z^2} + c_2 z^2 + c_4 z^4 + \cdots
	\]
	for some complex coefficients \(c_k\) (coming from the lattice).
	Then
	\[
	\wp'(z) = -\frac{2}{z^3} + 2c_2 z + 4c_4 z^3 + \cdots.
	\]
	
	So near \(z=0\),
	\[
	\omega = \left(-\frac{2}{z^3} + 2c_2 z + 4c_4 z^3 + \cdots\right)\,dz.
	\]
	
	In Laurent series form:
	\[
	\omega = -2 z^{-3} dz + 2c_2 z\,dz + 4c_4 z^3 dz + \cdots.
	\]
	
	Note there is \emph{no} term of the form \(c_{-1} z^{-1}dz\), so
	\[
	\Res_{z=0}(\omega) = 0.
	\]
	Similarly, at any other lattice point \(\lambda\in\Lambda\), shifting \(z\mapsto z-\lambda\)
	gives the same type of expansion: pole of order 3, no \(1/(z-\lambda)\) term.
	Thus
	\[
	\Res_{[0]}(\omega) = 0,\quad
	\Res_{[\lambda]}(\omega)=0\quad\text{in the quotient }X.
	\]
	
	\subsubsection*{Exactness and periods}
	
	Since \(\omega=d\wp\), it is an exact differential. On the torus, this implies
	for any closed loop \(\gamma\) in \(X\),
	\[
	\oint_{\gamma}\omega = \oint_{\gamma}d\wp = 0.
	\]
	This is the global version of the fact that an exact differential has zero
	integral over closed paths.
	
	\subsection{A very concrete elliptic function built from \(\wp\)}
	
	Fix some \(a\in\C\) with \([a]\neq[0]\) in \(X\), and also \([a]\neq[-a]\) (i.e.\
	\(2a\notin\Lambda\)). Consider the function
	\[
	g(z) = \wp(z) - \wp(a),
	\]
	which is \(\Lambda\)-periodic and meromorphic.
	
	Define:
	\[
	f(z) = \frac{\wp'(z)}{\wp(z) - \wp(a)}.
	\]
	This is a classical elliptic function: it is the derivative of the logarithm of
	\(g(z)\):
	\[
	f(z) = \frac{d}{dz}\log(\wp(z)-\wp(a)).
	\]
	
	\subsubsection*{Poles of \(f(z)\) on the torus \(X\)}
	
	\paragraph{At \(z=a\).}
	Near \(z=a\), write \(\zeta = z-a\). Then expand:
	\[
	\wp(z) = \wp(a) + \wp'(a)\zeta + \frac{1}{2}\wp''(a)\zeta^2 + \cdots.
	\]
	So
	\[
	\wp(z) - \wp(a) = \wp'(a)\zeta + \frac{1}{2}\wp''(a)\zeta^2 + \cdots.
	\]
	Similarly
	\[
	\wp'(z) = \wp'(a) + \wp''(a)\zeta + \cdots.
	\]
	
	Thus
	\[
	f(z) 
	= \frac{\wp'(z)}{\wp(z)-\wp(a)}
	= \frac{\wp'(a) + \wp''(a)\zeta + \cdots}
	{\wp'(a)\zeta + \frac{1}{2}\wp''(a)\zeta^2 + \cdots}.
	\]
	Pull out \(\wp'(a)\zeta\) from the denominator:
	\[
	f(z)
	= \frac{\wp'(a) + \wp''(a)\zeta + \cdots}
	{\wp'(a)\zeta\left(1 + \frac{\wp''(a)}{2\wp'(a)}\zeta + \cdots\right)}.
	\]
	Now expand:
	\[
	\frac{1}{1 + \alpha\zeta + \cdots} = 1 - \alpha\zeta + \cdots,
	\]
	so near \(\zeta=0\),
	\[
	f(z)
	\sim \frac{1}{\zeta} \cdot
	\frac{\wp'(a)}{\wp'(a)} = \frac{1}{\zeta} = \frac{1}{z-a}.
	\]
	Thus \(f\) has a \emph{simple pole} at \(z=a\) with residue
	\[
	\Res_{z=a}\bigl(f(z)\,dz\bigr) = 1.
	\]
	
	\paragraph{At \(z=-a\).}
	Because \(\wp\) is even and \(\wp'\) is odd,
	\[
	\wp(-z) = \wp(z),\quad \wp'(-z) = -\wp'(z).
	\]
	The equation \(\wp(z) = \wp(a)\) has the two solutions \(z = \pm a\) modulo \(\Lambda\).
	So \(\wp(z)-\wp(a)\) also vanishes at \(z=-a\). Repeating the same expansion, or
	just using the symmetry, we find
	\[
	\Res_{z=-a}\bigl(f(z)\,dz\bigr) = 1.
	\]
	
	\paragraph{At \(z=0\) (and other lattice points).}
	Near \(z=0\),
	\[
	\wp(z) \sim \frac{1}{z^2},\quad \wp'(z)\sim -\frac{2}{z^3}.
	\]
	Then
	\[
	f(z) = \frac{\wp'(z)}{\wp(z)-\wp(a)}
	\sim \frac{-2 z^{-3}}{z^{-2} - \wp(a)}
	= \frac{-2 z^{-3}}{z^{-2}(1 - \wp(a)z^2)}
	= \frac{-2}{z}\cdot\frac{1}{1 - \wp(a)z^2}.
	\]
	Expand \(\frac{1}{1 - \wp(a)z^2} = 1 + \wp(a)z^2 + \cdots\), so
	\[
	f(z) \sim \frac{-2}{z} + (\text{holomorphic terms}).
	\]
	Thus at \(z=0\) we have a simple pole with residue
	\[
	\Res_{z=0}\bigl(f(z)\,dz\bigr) = -2.
	\]
	
	Similarly, at other lattice points \(\lambda\neq 0\), the local behavior is
	like near 0 shifted by \(\lambda\), giving the same residue pattern, but on the
	torus \(X=\C/\Lambda\) all lattice points project to a finite set of points,
	and you can group residues within one fundamental domain.
	
	\subsubsection*{Residue theorem on the torus}
	
	On the compact Riemann surface \(X\),
	\[
	\sum_{p\in X} \Res_p\bigl(f(z)\,dz\bigr) = 0.
	\]
	From the computations:
	
	\begin{itemize}
		\item \(\Res_{[a]} = 1\),
		\item \(\Res_{[-a]} = 1\),
		\item \(\Res_{[0]} = -2\)
	\end{itemize}
	(and no other poles in a fundamental parallelogram),
	so
	\[
	1 + 1 - 2 = 0.
	\]
	This is a very concrete check of the residue theorem on a torus for this
	particular elliptic function.
	
	\subsection{Function field \(\M(\C/\Lambda)\) via \(\wp\) and \(\wp'\)}
	
	A fundamental theorem: \(\wp\) and \(\wp'\) satisfy
	\[
	(\wp'(z))^2 = 4\wp(z)^3 - g_2 \wp(z) - g_3,
	\]
	where \(g_2,g_3\) are complex constants depending on \(\Lambda\).
	
	If we set
	\[
	X := \wp(z),\quad Y := \wp'(z),
	\]
	then
	\[
	Y^2 = 4X^3 - g_2 X - g_3.
	\]
	
	From the differential-form viewpoint:
	\[
	dX = d\wp(z) = \wp'(z)\,dz = Y\,dz
	\quad\Rightarrow\quad
	dz = \frac{dX}{Y}.
	\]
	So the basic holomorphic 1-form \(dz\) on the torus becomes
	\[
	dz = \frac{dX}{\sqrt{4X^3 - g_2 X - g_3}},
	\]
	when we view the torus as the algebraic curve \(Y^2 = 4X^3 - g_2 X - g_3\).
	
	The function field is then
	\[
	\M(\C/\Lambda)
	= \C(\wp,\wp')
	\cong \C(X,Y)\big/\bigl(Y^2 - 4X^3 + g_2X + g_3\bigr).
	\]
	
	Concretely, any meromorphic function \(F\) on \(X\) is of the form
	\[
	F([z]) = R\bigl(\wp(z),\wp'(z)\bigr)
	\]
	for some rational function \(R(X,Y)\).
	
	Our explicit example
	\[
	f(z) = \frac{\wp'(z)}{\wp(z)-\wp(a)} = \frac{Y}{X - \wp(a)}
	\]
	is exactly such a rational function in \((X,Y)=(\wp,\wp')\), and we computed
	its poles and residues using differential-form techniques in detail.
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section*{Conclusion}
	
	\begin{itemize}
		\item For \(X=\CP^1\), we picked a very concrete rational function
		\(f(z)=(z-1)^2/(z(z-2))\), computed its divisor, wrote it via partial fractions,
		and computed \(df\) as a meromorphic 1-form, verifying the residue behavior.
		This illustrates \(\M(\CP^1)=\C(z)\).
		
		\item For \(X=\C/\Lambda\), we used \(\wp,\wp'\) and a very explicit elliptic
		function \(f(z)=\wp'(z)/(\wp(z)-\wp(a))\), expanded near poles, and computed residues of
		the meromorphic 1-form \(f(z)\,dz\). This illustrates concretely how
		\(\M(\C/\Lambda)\) is generated by \(\wp,\wp'\), and how differential forms
		(like \(\wp'(z)\,dz = d\wp(z)\)) control the structure of the function field.
	\end{itemize}
	
\end{document}
