\documentclass[12pt]{article}
\usepackage[margin=1.05in]{geometry}
\usepackage{amsmath,amsthm,amssymb}

\newtheorem{proposition}{Proposition}

\begin{document}
	
	\begin{proposition}
		Let $X$ be a Riemann surface and $f$ a holomorphic (resp.\ meromorphic) function on $X$.
		Then $u:=\log|f|$ is harmonic on $X\setminus (Z(f)\cup P(f))$.
		If $f$ is holomorphic and nowhere zero on all of $X$, then $u$ is harmonic on $X$; on compact, connected $X$
		this forces $f$ (hence $u$) to be constant.
	\end{proposition}
	
	\begin{proof}
		Fix a point $p\in X$ with $f(p)\neq 0$ (and $p$ not a pole if $f$ is meromorphic). Take a small simply connected
		neighborhood $U$ of $p$ on which $f$ has no zeros or poles. On $U$ the holomorphic $1$-form $\frac{f'}{f}\,dz$
		is exact, so there exists a holomorphic function $g$ on $U$ with $g'=\frac{f'}{f}$ and $e^{g}=f$.
		Write $g=\varphi+i\psi$ with real-valued $\varphi,\psi$. Then on $U$,
		\[
		|f| = |e^{g}| = e^{\Re g} = e^{\varphi}\qquad\Longrightarrow\qquad u=\log|f|=\varphi.
		\]
		But the real part of a holomorphic function is harmonic (equivalently, $\varphi_{xx}+\varphi_{yy}=0$ in any
		local coordinate), hence $u$ is harmonic on $U$. Since $p$ was arbitrary in $X\setminus (Z(f)\cup P(f))$,
		$u$ is harmonic there.
		
		If $f$ is holomorphic and nowhere zero on all of $X$, then the above holds on all of $X$.
		If, in addition, $X$ is compact and connected, any harmonic function is constant (e.g.\ by the maximum
		principle or by integrating $|\nabla u|^2$ and using Stokes), so $u$ is constant and therefore $f$ has
		constant modulus. A holomorphic map with constant modulus is constant (by the open mapping theorem),
		so $f$ is constant.
	\end{proof}
	
	\noindent\textbf{Remark (meromorphic case, distributional Laplacian).}
	If $f$ is meromorphic, near a zero or pole at $p$ of order $m\in\mathbb{Z}$ one can write
	$f(z)=z^{m}g(z)$ with $g$ holomorphic and $g(0)\neq 0$. Then
	$\log|f|= m\log|z|+\log|g|$, where $\log|g|$ is harmonic and
	$\Delta\log|z|=2\pi\,\delta_{0}$ (distributionally). Hence
	\[
	\Delta \log|f| \;=\; 2\pi\sum_{p\in X} \operatorname{ord}_p(f)\,\delta_p
	\]
	as distributions. This shows $\log|f|$ is subharmonic globally and harmonic away from zeros and poles.
\end{document}
